Dynamic Transition Analysis with TIMES

### 2019-01-07 doc/2019-01-poster/poster.tex
adjusted title spacing

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

>>>>

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube\inst{1}, Andrew Chapman\inst{2}, James Stubbins\inst{1}, \textbf{Kathryn Huff}\inst{1}}
\institute[shortinst]{ \inst{1} University of Illinois at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, USA \and \inst{2} International Institute for Carbon Neutral Energy Research (I$^2$CNER), Kyushu University, Fukuoka, Japan}
%----------------------------------------------------------------------------------------
